Lab 0006: Latent Dirichlet Allocation Applied to Revisions

### 2008-10-24 lda-paper.tex
2008-10-24 10:44:28 abez

Topic analysis of fine-grained revisions is important as often
revisions belonging to different topics are interleaved or even mixed
inside of commits.

@@

@@

@@

Often words are shared across topics, see talbe \ref{tab:portability}
for tracking topics about portability.

@@

%LDA Skeleton
%1. [ ] Abstract 
\begin{abstract}
\end{abstract}
%2. [ ] Introduction
\section{Introduction}

%3. [ ] Previous Work [0/2]
\section{Previous Work}
%   1. [ ] Intro to LDA
\subsection{Intro to LDA}
%   2. [ ] LDA Work [0/6]
\subsection{LDA Work}
%      1. [ ] LDA itself
%      2. [ ] Maletic stuff
%      3. [ ] WCRE: Scott/Jim
%      4. [ ] WCRE: Bug LDA stuff
%      5. [ ] MSR: Challenge work
%      6. [ ] FCA work
%4. [ ] Methodology [0/9]
\section{Methodology}
%   1. [ ] Extract Repos
\subsection{Extract Repos}
%   2. [ ] Extract Documents
\subsection{Extract Documents}
%   3. [ ] Windowed Sets
\subsection{Windowed Sets}
%   4. [ ] Cluster Windowed Set w/ LDA
\subsection{Cluster Windowed Set w/ LDA}
%   5. [ ] Extract Clusters
\subsection{Extract Clusters}
%   6. [ ] Cluster Similarity [0/1]
\subsection{Cluster Similarity}
%      1. [ ] need the tool
%             grab from the cluster analysis
%   7. [ ] Continuous Cluster Analysis
\subsection{Continuous Cluster Analysis}
%   8. [ ] Topic Smear
\subsection{Topic Smear}
%   9. [ ] Visualization [0/1]
\subsection{Visualization}
%       1. [ ] need the visualizer
%5. [ ] Tools [0/5]
\section{Tools}
%   1. [ ] LDA
\subsection{LDA}
%   2. [ ] Extractor
\subsection{Extractor}
%   3.   Similarity
\subsection{Similarity}
%   4.   Smearing
\subsection{Smearing}
%   5.   Visualizer
\subsection{Visualizer}
%6.   Results [0/4]
\section{Results}
%   1. Interesting smears 
%   2.   postgresql
\subsection{Postgresql}
%   3.   mysql
\subsection{Mysql}
%   4.   firebird
\subsection{Firebird}
%   5.   what's that other db?
\subsection{ what's that other db?}
%7.   Validation [0/1]
\subsection{Validation}
%   1. well i'm stumped
%   2. look at it?
%   3. investigate those revisions and check the proportion etc
%   4. exploratory
%   5.   work it out
%8.   Validity Threats [0/5]
\section{Validity Threats}
%   1.   validation
%   2.   LDA is questionable
%   3.   blackbox problem
%   4.   not in the token
%   5.   multiple X token
%9.    Future Work
\section{ Future Work}
%10.   Conclusions
\section{Conclusions}
%11.   Start file file:/home/abez/projects/lda-paper/lda-paper.tex

>>>>

Topic analysis of fine-grained revisions is important as often
revisions belonging to different topics are interleaved or even mixed
inside of commits. Using powerful topic analysis like Latent Semantic
Indexing (LSI) or Latent Dirichlet Allocation (LDA) one can seperate
these mixed signals into coherent topics. In this case a topic is a
set of tokens that are related to each other.

\section{Previous Work}
%   1. [ ] Intro to LDA
\subsection{Intro to LDA}

\subsection{LDA Work}
%      1. [ ] LDA itself
%      2. [ ] Maletic stuff
%      3. [ ] WCRE: Scott/Jim
%      4. [ ] WCRE: Bug LDA stuff
%      5. [ ] MSR: Challenge work
%      6. [ ] FCA work
%4. [ ] Methodology [0/9]

@@

\subsection{Extract Repos}
%   2. [ ] Extract Documents
\subsection{Extract Documents}
%   3. [ ] Windowed Sets
\subsection{Windowed Sets}
%   4. [ ] Cluster Windowed Set w/ LDA
\subsection{Cluster Windowed Set w/ LDA}
%   5. [ ] Extract Clusters
\subsection{Extract Clusters}
%   6. [ ] Cluster Similarity [0/1]
\subsection{Cluster Similarity}
%      1. [ ] need the tool
%             grab from the cluster analysis
%   7. [ ] Continuous Cluster Analysis
\subsection{Continuous Cluster Analysis}
%   8. [ ] Topic Smear
\subsection{Topic Smear}
%   9. [ ] Visualization [0/1]
\subsection{Visualization}
%       1. [ ] need the visualizer

@@

%   1. [ ] LDA

%   2. [ ] Extractor

%   3.   Similarity

%   4.   Smearing

%   5.   Visualizer

@@

Often words are shared across topics, see table \ref{tab:portability}
for tracking topics about portability.

@@

%LDA Skeleton
%1. [ ] Abstract 
%2. [ ] Introduction

%3. [ ] Previous Work [0/2]
%   2. [ ] LDA Work [0/6]
\section{Results}
%   1. Interesting smears 
%   2.   postgresql
\subsection{Postgresql}
%   3.   mysql
\subsection{Mysql}
%   4.   firebird
\subsection{Firebird}
%   5.   what's that other db?
\subsection{ what's that other db?}
%7.   Validation [0/1]
\subsection{Validation}
%   1. well i'm stumped
%   2. look at it?
%   3. investigate those revisions and check the proportion etc
%   4. exploratory
%   5.   work it out
%8.   Validity Threats [0/5]
\section{Validity Threats}
%   1.   validation
%   2.   LDA is questionable
%   3.   blackbox problem
%   4.   not in the token
%   5.   multiple X token
%9.    Future Work
\section{ Future Work}
%10.   Conclusions
\section{Conclusions}
%11.   Start file file:/home/abez/projects/lda-paper/lda-paper.tex
